Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-02-25 main.Rmd
Monash working paper template

authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  thanks: "Email: Sayani.Gupta@monash.edu"

- name: Rob J Hyndman
  affiliation: Department of Econometrics and Business Statistics, Monash University

- name: Dianne Cook
  affiliation: Department of Econometrics and Business Statistics, Monash University

- name: Antony Unwin
  affiliation: University of Augsburg

keywords:
- data visualization
- statistical distributions
- time granularities
- calendar algebra
- periodicties
- grammar of graphics
- R

@@

   Visualizing data across granularities which are either single-order-up or multiple-order-up or periodic/aperiodic helps us to understand periodicities, pattern and anomalies in the data. Because of the large volume of data available, using displays of probability distributions conditional on one or more granularities is a potentially useful approach. This work provides tools for creating granularities and exploring the associated time series within a tidy workflow, so that probability distributions can be examined using the range of graphics available in ggplot2 [@Wickham2009pk].
bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,longtable,todonotes}
  \def\mod{~\text{mod}~}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(tsibble)
library(gravitas)
library(tsibble)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

@@

# cyclic time granularities {#sec:cyclic-gran}

>>>>

author:
  - familyname: Gupta
    othernames: Sayani
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia. \newline \newline CSIRO Data61, \newline Private Bag 10, South Clayton, VIC 3169
    email : Sayani.Gupta@monash.edu
  - familyname: Hyndman
    othernames: Rob J
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : rob.hyndman@monash.edu
  - familyname: Cook
    othernames: Dianne
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : dicook@monash.edu
  - familyname: Unwin
    othernames: Antony
    address: University of Augsburg
    email : au50au@me.com

keywords: "data visualization, statistical distributions, time granularities, calendar algebra, periodicties, grammar of graphics, R"

@@

   Visualizing data across granularities which are either single-order-up or multiple-order-up or periodic/aperiodic helps us to understand periodicities, pattern and anomalies in the data. Because of the large volume of data available, using displays of probability distributions conditional on one or more granularities is a potentially useful approach. This work provides tools for creating granularities and exploring the associated time series within a tidy workflow, so that probability distributions can be examined using the range of graphics available in ggplot2 [@Wickham2009pk].
toc: false
bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,longtable,todonotes}
  \def\mod{~\text{mod}~}
biblio-style: authoryear-comp
output:
  #bookdown::pdf_book:
    MonashEBSTemplates::workingpaper:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes

---

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(tsibble)
library(gravitas)
library(tsibble)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)})
```

@@

# Cyclic time granularities {#sec:cyclic-gran}
